\ttitle

### 2013-01-30 Chapters/Chapter2.tex
Setup for PCA

\subsection{Principal Component Analysis}

>>>>

\subsection{Principal Component Analysis}
When working with simple 2- or 3-dimensional data it is often, for humans, 
easy to discover patterns in the set. The data can be plotted and the lines or 
planes among which the data points lie gives an indication of the pattern. 
With Principal Component Analysis (PCA) this process is also easy for 
automated systems. With this method the overall form of a set of data points 
can be represented, the most discriminative dimensions can be found, the 
dimensionality of a set can be reduced (which yield in data compression) or 
the result can be used to characterize and differentiate sets of data points.

The workings of the PCA \cite{smith2002tutorial} relies on the concepts of 
standard deviation, 
covariance, eigenvectors and eigenvalues of matrices. These concepts will be 
discussed very briefly. The standard deviation of a set is an measure for the 
spread around the mean for a single dimension, or feature. The covariance 
between two features indicates how they are related; when positive the two 
features will increase together; when negative one will decrease when the 
other increases and when zero they are unrelated.
*** [eigenvectors]
*** [eigenvalues]

***
[purpose: dimensionality reduction, most discriminative dimensions. Difference 
in dimensionality.]
